Model

### 2019-05-13 stats/model.Rmd
model predictions that make sense

  var speakerOptimalityParameters = {
    intercept: uniformDrift({a: -2, b: 2, width: 0.5}),
    slope: uniformDrift({a: -2, b: 2, width: 0.5})
  }

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "incrementalMH", 
                        samples = 2000, 
                        burn = 1000,
                        verbose = T,
                        #lag = 1,
                        verboseLag = 1000)
)

saveRDS(sem_know_model, "../saves/sem_know_model.rds")
sem_know_model <- readRDS("../saves/sem_know_model.rds")

@@

model_pred <- sem_know_model %>%
  separate(Parameter, into = c("type", "item","x"))%>%
  filter(type == "modelPrediction")%>%
  separate(value, into = c("age", "pred"),sep = ", ")%>%
  mutate(age = as.numeric(str_remove_all(age, "[(c]")),
         pred = as.numeric(str_remove(pred, "[)]")))%>%
  select(-x)

@@

model_pred_summary <- model_pred %>%
  group_by(item,age)%>%
  summarise(mode = estimate_mode(pred),
            uci = hdi_upper(pred),
            lci = hdi_lower(pred))

@@

```{r}
plot_model_pred <- model_pred_summary%>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Inverse Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()

@@

@@

p2 <- read_csv("../data/child_basic_me.csv")%>%
  filter(trial != "train1",
         trial != "train2")%>%
  mutate(item = familiar)%>%
    left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiar = fct_reorder(factor(item), mean_aoa))

data_plot
```

```{r}
ggarrange(data_plot,inv_model_plot,model_plot, common.legend = T, legend = "right", nrow = 1, ncol = 3)
```

>>>>

  var speakerOptimalityParameters = {
    intercept: uniformDrift({a: -2, b: 2, width: 0.5}),
    slope: uniformDrift({a: 0, b: 2, width: 0.5})
  }

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH", 
                        samples = 6000, 
                        burn = 2000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
sem_know_model <- readRDS("../saves/sem_know_model.rds")

@@

# model_pred <- sem_know_model %>%
#   separate(Parameter, into = c("type", "item","x"))%>%
#   filter(type == "modelPrediction")%>%
#   separate(value, into = c("age", "pred"),sep = ", ")%>%
#   mutate(age = as.numeric(str_remove_all(age, "[(c]")),
#          pred = as.numeric(str_remove(pred, "[)]")))%>%
#   select(-x)

@@

# model_pred_summary <- model_pred %>%
#   group_by(item,age)%>%
#   summarise(mode = estimate_mode(pred),
#             uci = hdi_upper(pred),
#             lci = hdi_lower(pred))

@@

```{r}
# plot_model_pred <- model_pred_summary%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))

model_plot <- ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Inverse Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()

@@

```{r}
p2 <- read_csv("../data/child_basic_me.csv")%>%
  filter(trial != "train1",
         trial != "train2")%>%
  mutate(item = familiar)%>%
    left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiar = fct_reorder(factor(item), mean_aoa))

```
```{r}
ggarrange(data_plot,model_plot, common.legend = T, legend = "right", nrow = 1, ncol = 2)
```

@@
